Tropical Andes IUCN Montane and Lowland forest

### 2023-08-03 code/L0/L0_TropicalAndes_IUCNhabitatClassification.Rmd
correct spelling errors Reclassify forest raster to keep cells with values over 500 remove shapefile code

```{r}
# crop moist montane to tropical andes
iucn_moist_montane_forest_crop <- crop(iucn_moist_montane_forest, study_region)
TA_iucn_moist_montane_forest <- mask(iucn_moist_montane_forest_crop, study_region)
plot(TA_iucn_moist_montane_forest)
TA_iucn_moist_montane_forest
```

```{r}
#crop moist lowland to tropical andes
iucn_moist_lowland_forest_crop <- crop(iucn_moist_lowland_forest, study_region)
TA_iucn_moist_lowland_forest <- mask(iucn_moist_lowland_forest_crop, study_region)
plot(TA_iucn_moist_lowland_forest)
TA_iucn_moist_lowland_forest
```

```{r}
# combine TA_iucn_moist_lowland_forest & TA_iucn_moist_montane_forest into one raster
TA_iucn_habitat_forest <- merge(TA_iucn_moist_lowland_forest, TA_iucn_moist_montane_forest)
plot(TA_iucn_habitat_forest)
TA_iucn_habitat_forest
```

@@

# Convert to sf
```{r}
# convert to SpatRaster
TA_iucn_habitat_forest_sr <- as(TA_iucn_habitat_forest, "SpatRaster")
TA_iucn_habitat_forest_sr
```

```{r}
TA_iucn_habitat_forest_sv <- as.polygons(TA_iucn_habitat_forest_sr)
TA_iucn_habitat_forest_sv
plot(TA_iucn_habitat_forest_sv)
```

```{r}
TA_iucn_habitat_forest_shape <- sf::st_as_sf(TA_iucn_habitat_forest_sv)
TA_iucn_habitat_forest_shape
plot(TA_iucn_habitat_forest_shape)
```

# Save shapefile
```{r}
st_write(TA_iucn_habitat_forest_shape, file.path(output_path, "TropicalAndes_IUCNHabitat_Forest.shp"), overwrite=TRUE)
```

>>>>

# Crop moist montane to Tropical Andes
```{r}
iucn_moist_montane_forest_crop <- crop(iucn_moist_montane_forest, study_region)
TA_iucn_moist_montane_forest <- mask(iucn_moist_montane_forest_crop, study_region)
plot(TA_iucn_moist_montane_forest)
TA_iucn_moist_montane_forest
```

# Crop moist lowland to Tropical Andes
```{r}
iucn_moist_lowland_forest_crop <- crop(iucn_moist_lowland_forest, study_region)
TA_iucn_moist_lowland_forest <- mask(iucn_moist_lowland_forest_crop, study_region)
plot(TA_iucn_moist_lowland_forest)
TA_iucn_moist_lowland_forest
```

# Combine TA_iucn_moist_lowland_forest & TA_iucn_moist_montane_forest into one raster
```{r}
TA_iucn_habitat_forest <- merge(TA_iucn_moist_lowland_forest, TA_iucn_moist_montane_forest)
plot(TA_iucn_habitat_forest)
TA_iucn_habitat_forest
```

# Reclassify forest raster with values above 500 to one value and less than 500 to NA
```{r}
mat <- c(0, 500, NA,
        500, 1000, 1)
rclmat <- matrix(mat, ncol = 3, byrow = TRUE)
TA_iucn_habitat_forest <- reclassify(TA_iucn_habitat_forest, rclmat)
TA_iucn_habitat_forest
plot(TA_iucn_habitat_forest)
```

@@
